### 2023-01-27 paper-reviews/papers-2023.tex
Add mobileye article

>>>>

\section*{Autonomous Driving}
\begin{itemize}
    \item The article present an overview of Mobileye existing and in flight processors for advanced-driver-assistance-systems (ADAS). The article also presents a simplistic comparison with Nvidia GPU-based solutions for the area. The main comparison metrics are trillion operations per second (TOPS) and efficiency which is measured as TOPS divided by power consumption. It is an overall nice basic overview of what is happening in the area with cool examples of 360-degree image construction and object classification:

    \cite{Delmer:Mobileye:2019}.
\end{itemize}
